Incentivizing Exploration with Unbiased Histories

### 2019-04-29 intro.tex
Minor edit.

\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement). However, these assumptions appear quite problematic in the context of recommendation systems of actual online websites such as those mentioned above. In particular, much of the prior work suggests disclosure policies that merely recommend an action to each user, without any other supporting information, and moreover recommend exploratory actions to some randomly selected users. This works out extremely well in theory, but it is very unclear whether users would even know some complicated policy of the principal, let alone trust the principal to implement the stated policy. Even if they do know the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally.
%
Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement,%
\footnote{\asedit{Large-scale systems that implement bandit algorithms can be notoriously difficult to debug \cite{DS-arxiv}.}}
 whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration. Regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.

>>>>

\xhdr{Our scope.} Prior work on incentivizing exploration, with or without monetary incentives, achieves much progress (more on this in ``related work"), but relies heavily on the standard assumptions of Bayesian rationality and the ``power to commit" (\ie users trust that the principal actually implements the policy that it claims to implement). However, these assumptions appear quite problematic in the context of recommendation systems of actual online websites such as those mentioned above. In particular, much of the prior work suggests disclosure policies that merely recommend an action to each user, without any other supporting information, and \asedit{sometimes recommend exploratory actions}. This works out extremely well in theory, but it is very unclear whether users would know and  understand some complicated policy deployed by the principal, let alone trust the principal to implement this policy. Even if they do understand the policy and trust that it was implemented as claimed, it's unclear whether users would react to it rationally.
%
Several issues are in play: to wit, whether the principal intentionally uses a different disclosure policy than the claimed one (\eg because its incentives are not quite aligned with the users'), whether the principal correctly implements the policy that it wants to implement,%
\footnote{\asedit{Large-scale systems that implement bandit algorithms can be notoriously difficult to debug \cite{DS-arxiv}.}}
 whether the users trust the principal to make correct inferences on their behalf, and whether they find it acceptable that they may be singled out for exploration. Regardless of how the users react to such disclosure policies, they may prefer not to be subjected to them, and leave the system.
